---
title: "Mission Impossible 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import via a csv

Import the csv file called "mi2DataAll".

```{r}
library(readr)
gdp <- read_csv("mi2DataAll.csv")
gdp
```

# Delete the column

Delete the column "X1".

```{r}
  # Columns
 
gdp$X1 <- NULL
gdp
```

# Remove missing values

Remove all missing values from the dataframe "gdp".

```{r}
gdp2 <- tidyr::drop_na(gdp)
```

# Gather the data

You need to gather (modify from wide to long) the dataframe "gdp2" to get three column: "country", "year", "gdp".

```{r}
library(tidyr)

gdp3 <- tidyr::gather(gdp2, "year", "gdp", 2:59)
gdp3
```

# Filter the data

Filter the data to only keep the following countries: "united states", "canada", "japan", "belgique", "FRA".

```{r}
library(dplyr)
gdp4 <- dplyr::filter(gdp3, country == "united states" | country == "canada" | country == "japan" | country == "belgique" | country == "FRA")
gdp4
```

# Import via a gsheet 

Import the data containing the longitute and latitude from this gsheet : <https://docs.google.com/spreadsheets/d/1VUxLOL2GH2ULrZ-lqQUa5IPKeSH-4dy_hTevZUyqbv4/edit#gid=0>

```{r}
library(gsheet)
locations <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1VUxLOL2GH2ULrZ-lqQUa5IPKeSH-4dy_hTevZUyqbv4/edit#gid=0")
locations
```

# Combining tables

Join the data frame "locations" to the data frame "gdp4". Before combining the data frames, make sure that all countries and columns have the same names!

```{r}
library(base)
gdp4$country <- gsub("FRA","France",gdp4$country)
gdp4$country <- gsub("belgique","Belgium",gdp4$country)
gdp4$country <- gsub("Japan","japan",gdp4$country)
gdp4$country <- gsub("United States","united states",gdp4$country)
gdp4$country <- gsub("canada","Canada",gdp4$country)
gdp4

library(dplyr)
locations=rename(locations, country = "Pays")
gdp5 <- left_join(gdp4, locations, by = "country")
gdp5
```

# Delete a column

Delete the column "Continent".

```{r}
gdp5$Continent <- NULL
gdp5

```

















